\documentclass{article}
\begin{document}

MAKERERE  UNIVERSITY

COLLEGE OF COMPUTING AND INFORMATION SCIENCES

SCHOOL OF COMPUTING AND INFORMATICS TECHNOLOGY

Compiled By
KAMUGISHA KEITH
12/U/6112/PS
212012455

TITLE: HOW TO BEAT THE UGANDAN HEAT.



1.	Introduction

Of late it has been scorching hot that people must move with water to drinking even when the distance they are going to take is short. Form people with vehicles driving with air conduction to pedestrians putting on all kinds on head gear to beat the heat.

2.	During the night time

\begin{itemize}
\item With this heat, even when the sun sets it’s still shockingly hot. So, when you can’t sleep try these;
\item Put an ice packs in front of a fan and the breeze that you with feel on your skin will be cool instead of the hot breeze from the already hot air in the room. If you happen to be in a room with AC then this is the almost the same effect you will experience. 
\item Keep a wet (dump) cloth by your bed and apply to the neck and face can help cool you down just like when you have fewer the same method helps to reduce the body temperature.
\item If you’re in a safe neighborhood, you can open the window so that fresh air drives out the hot air in the room.
\item Sleep naked or with less clothing on your body to allow the body to easily loose body heat through the skin poses. 
\end{itemize}

3.	During the day

\begin{itemize}
\item Dress light. This helps air to easily penetrate the cloths to and from the skin and hence help to cool the body in the process.
\item Spend time in a shade when you’re not moving because the shade is cooler than the areas the sun is beaming on.
\item Drinking a lot of water to help in the sweating and hence cool the body.
\item Get a hat and plan not to move when the sun is directly overhead because that’s when the day is at its hottest.
\item Swimming can help keep the body cool and it’s a lot of fun to do.
\item Take a cool shower twice a day if you have time because this lowers the body temperature and help make you feel fresh
\end{itemize}

4.	How to reduces the heat.

The general temperature in the country is raising, and the dry and wet seasons are changing (with dry season now longer than the wet season). So here are some ways of reducing the heat;

\begin{itemize}
\item We also know we need the forests to help in the rain fall formation, so we need to plan on trees and reduces on the deforestation.
\item We need to stop using old technology for fueling our homes like fire wood or charcoal and adopt new energy resources like electricity and gas this will help reduce on the pressure the vegetation.
\item We the help of the governing bodies in place we need to protect the environment vegetation through planning for the growing population. 
\end{itemize}

Conclusion 
So, unless we work together to change the damage we are doing to the environment we should prepare for higher temperatures. 


\end{document}